---
#output: stevetemplates::cv
output: 
  pdf_document:
    template: my-template.tex
latex_engine: pdflatex
geometry: margin=1in

title: "CV"
author: Em Heffernan

jobtitle: "PhD Candidate, University of Toronto"
fontawesome: yes
email: e.maeve.heffernan@gmail.com
# github: svmiller
# twitter: em_heffernan
# osf: "Enter 5 digit osf string here"
phone: "705 434 8655"
web: emheffernan.github.io
updated: FALSE
rdateformat: "`r format(Sys.time(), '%d %b %Y')`"

bibliography: CV_Pubs.bib
csl: apa-cv.csl
nocite: (@*)

keywords: R Markdown, academic CV, template

fontfamily: montserrat
fontfamilyoptions: defaultfam
fontsize: 10pt
linkcolor: blue
urlcolor: blue

params:
  pdf_mode:
    value: true

# header-includes:
#   - \usepackage[defaultfam,tabular,lining]{montserrat}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
library(tinytex)
source("cv_printing_functions.r")
library(vitae);library(tibble);library(tufte)


# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1WgfzqcE2shTZ1QICDNYhCWhuOU8HAZfZwL3r89Ea0b0/edit#gid=917338460",  
  pdf_mode = params$pdf_mode
)

```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(fontawesome)
```

```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

# `r fa("graduation-cap", fill = "black")` Education

```{r}
CV %<>% print_section('education')
```

# `r fa("award", fill = "black")` Awards

```{r}
CV %<>% print_section('awards')
```

# `r fa("microscope", fill = "black")` Research Experience

```{r}
CV %<>% print_section('research_positions')
```

# `r fa("briefcase", fill = "black")` Industry Experience

<!-- ::: aside -->

<!-- ```{r} -->

<!-- CV %<>% print_text_block('industy_experience_aside') -->

<!-- ``` -->

<!-- ::: -->

```{r}
CV %<>% print_section('industry_positions')
```

<!-- These breaks just force a new page so section doesnt get cut off -->

<br> <br> <br>

# `r fa("chalkboard-teacher", fill = "black")` Teaching Experience

<!-- ::: aside -->

<!-- ```{r} -->

<!-- CV %<>% print_text_block('teaching_experience_aside') -->

<!-- ``` -->

<!-- ::: -->

```{r}
CV %<>% print_section('teaching_positions')
```

# `r fa("users", fill = "black")` Volunteer Experience

<!-- ::: aside -->

<!-- ```{r} -->

<!-- CV %<>% print_text_block('volunteer_experience_aside') -->

<!-- ``` -->

<!-- ::: -->

```{r}
CV %<>% print_section('volunteer_experience')
```

# `r fa("comment-alt", fill = "black")` Presentations

**Academic Talks**

```{r}
CV %<>% print_section('presentations_talks')
```

**Posters**

```{r}
CV %<>% print_section('presentations_posters')
```

**Other Presentations**

```{r}
CV %<>% print_section('presentations_other')
```

<!-- # Peer-reviewed Publications -->

<!-- ```{r} -->

<!-- bibliography_entries("CV_Pubs.bib") -->

<!-- ``` -->

# `r fa("file-alt", fill = "black")` Peer-Reviewed Publications
<!-- ```{r} -->
<!-- bibliography_entries("CV_pubs.bib")  -->
<!-- ``` -->
